module2_eco_pol_factors

### 2022-03-11 moduletwoanalysis.Rmd
knit to html

---
title: "module2_eco_pol_factors"
output:
  word_document: default
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

summary(ecopolscale_pca)

>>>>

---
title: "module2_eco_pol_factors"
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

summary(ecopolscalepca)
